The Disk Wind Contribution to Optical Lines in Cataclysmic Variables

### 2013-11-29 paper.tex
Edited makefile and title

\title{The Disk Wind Contribution to Optical Lines in Cataclysmic Variables}
\author{J. H.
  Matthews, C. Knigge, K. S. Long, S. A. Sim \& N. Higginbottom}
%%\altaffiltext{1}{School of Physics \& Astronomy, University of Southampton,
  %%Southampton, SO17 1BJ, UK}

@@

>>>>

\title[Optical Lines from CV Disk Winds]
{The Disk Wind Contribution to Optical Lines in Cataclysmic Variables}

\author[Matthews et al.]{J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk},C.~Knigge,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and N.~Higginbottom$^1$
\medskip  
\\$^1$School of Physics and Astronomy, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom
\\$^2$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD, 21218
\\$^3$School of Mathematics and Physics, Queens University Belfast, University Road, Belfast, BT7 1NN, Northern Ireland, UK}

\date{\today}

@@

\begin{keywords}
Cataclysmic Variables - quasars: absorption lines - radiative transfer - 
methods: numerical.
\end{keywords}
